How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-05-01 tse-paper/content.tex
Commenting out

%% REVIEW MARKER
% Alt:
%\section{Analyzing Build Logs with Chunk Retrieval Techniques}
\section{Chunk Retrieval Techniques}
\label{sec:techniques}
% tense: past? except for general definitions / statements

% TODO This introduction is weird
In this section, we formally define the concept of chunk
retrievals from build logs.
Then, we motivate and present the choice of three such techqniues that
we implemented for this study in detail.

In this section,
we propose three so-called \emph{chunk retrieval techniques},
which retrieve a specific substring (chunk)
from a build log
% TODO passive ....
The techniques we propose run automatically
and can be easily configured through examples.
% TODO this should go under characteristics and not be in an introduction
to the section ...
An example in this case consists of a build log together with the
chunk that should be retrieved.
A user---a developer or a researcher who wants to analyze
build logs---provides these examples, which are easy to
adapt whenever the analysis technique needs
to support new cases.

>>>>

% Alt:
%\section{Analyzing Build Logs with Chunk Retrieval Techniques}
\section{Chunk Retrieval Techniques}
\label{sec:techniques}
% tense: past? except for general definitions / statements

In this section, we formally define the concept of chunk
retrievals from build logs.
Then, we motivate and present the choice of three such techqniues that
we implemented for this study in detail.

% TODO Caro: Not sure what to do with this ...
%% In this section,
%% we propose three so-called \emph{chunk retrieval techniques},
%% which retrieve a specific substring (chunk)
%% from a build log
%% % TODO passive ....
%% The techniques we propose run automatically
%% and can be easily configured through examples.
%% % TODO this should go under characteristics and not be in an introduction
%% to the section ...
%% An example in this case consists of a build log together with the
%% chunk that should be retrieved.
%% A user---a developer or a researcher who wants to analyze
%% build logs---provides these examples, which are easy to
%% adapt whenever the analysis technique needs
%% to support new cases.
